\RequirePackage{fix-cm}
\documentclass[titlepage]{article}

\usepackage{fullpage}   % Use the whole page
\usepackage{fancyhdr}   % Nice headers/footers
\usepackage{graphicx}   % Importing graphics
\usepackage{mdwlist}    % For itemize* and enumerate*
\usepackage{hyperref}   % Hyperlink references and URLs
\usepackage{subfig}
\usepackage{appendix}
\usepackage{listings}
%\usepackage{todonotes}
\usepackage{tikz}
\usepackage{pgf}
\usepackage{scalefnt}
\usepgfmodule{shapes}
\usepgfmodule{plot}
\usetikzlibrary{decorations}
\usetikzlibrary{arrows}
\usetikzlibrary{snakes}

\newcommand{\logo}{
	\pgfsetlinewidth{3pt}

	% Background
	\color{cyan!70!black}
	\pgfpathmoveto{\pgfpointxy{-5}{2}}
	\pgfpathlineto{\pgfpointxy{-5}{11}}
	\pgfpathlineto{\pgfpointxy{-2}{11.9}}	
	\pgfpathlineto{\pgfpointxy{2}{11.9}}	
	\pgfpathlineto{\pgfpointxy{5}{11}}
	\pgfpathlineto{\pgfpointxy{5}{2}}
	\pgfpathclose 
	\pgfusepath{fill,stroke} 

	% Base
	\color{green!70!black}
	\pgfsetstrokecolor{black}
	\pgfpathmoveto{\pgfpointxy{-2}{1.5}}
	\pgfpathcurveto{\pgfpointxy{-2}{1.5}}{\pgfpointxy{-6}{1.5}}{\pgfpointxy{-6}{2.5}}
	\pgfpathlineto{\pgfpointxy{-6}{4}}
	\pgfpathlineto{\pgfpointxy{6}{4}}
	\pgfpathlineto{\pgfpointxy{6}{2.5}}
	\pgfpathcurveto{\pgfpointxy{6}{1.5}}{\pgfpointxy{2}{1.5}}{\pgfpointxy{2}{1.5}}
	\pgfpathclose 
	\pgfusepath{fill,stroke} 
	
	% Curtains
	\color{red!70!black}
	\pgfsetstrokecolor{black}
	
	% Left
	\pgfpathmoveto{\pgfpointxy{-6}{11}}
	\pgfpathlineto{\pgfpointxy{-6}{2.5}}
	\pgfpathcurveto{\pgfpointxy{-6}{2.2}}{\pgfpointxy{-3.5}{2.2}}{\pgfpointxy{-3.5}{2.5}}
	\pgfpathcurveto{\pgfpointxy{-3.5}{3}}{\pgfpointxy{-3.5}{4}}{\pgfpointxy{-4.5}{5}}
	\pgfpathcurveto{\pgfpointxy{-2.5}{7}}{\pgfpointxy{-4}{11}}{\pgfpointxy{-3}{11.5}}
	\pgfpathcurveto{\pgfpointxy{-4}{11}}{\pgfpointxy{-2.5}{7}}{\pgfpointxy{-4.5}{5}}
	\pgfpathcurveto{\pgfpointxy{-2.5}{7}}{\pgfpointxy{-6}{11}}{\pgfpointxy{-3}{11.5}}
	\pgfpathcurveto{\pgfpointxy{-6}{11}}{\pgfpointxy{-2.5}{7}}{\pgfpointxy{-4.5}{5}}
	\pgfpathcurveto{\pgfpointxy{-2.5}{7}}{\pgfpointxy{-8}{11}}{\pgfpointxy{-3}{11.5}}
	\pgfpathcurveto{\pgfpointxy{-8}{11}}{\pgfpointxy{-2.5}{7}}{\pgfpointxy{-4.5}{5}}
	\pgfpathcurveto{\pgfpointxy{-2.5}{7}}{\pgfpointxy{-2.5}{11}}{\pgfpointxy{-3}{11.5}}
	\pgfusepath{fill,stroke}

	% Right
	\pgfsetlinewidth{3pt}
	\pgfpathmoveto{\pgfpointxy{6}{11}}
	\pgfpathlineto{\pgfpointxy{6}{2.5}}
	\pgfpathcurveto{\pgfpointxy{6}{2.2}}{\pgfpointxy{3.5}{2.2}}{\pgfpointxy{3.5}{2.5}}
	\pgfpathcurveto{\pgfpointxy{3.5}{3}}{\pgfpointxy{3.5}{4}}{\pgfpointxy{4.5}{5}}
	\pgfpathcurveto{\pgfpointxy{2.5}{7}}{\pgfpointxy{4}{11}}{\pgfpointxy{3}{11.5}}
	\pgfpathcurveto{\pgfpointxy{4}{11}}{\pgfpointxy{2.5}{7}}{\pgfpointxy{4.5}{5}}
	\pgfpathcurveto{\pgfpointxy{2.5}{7}}{\pgfpointxy{6}{11}}{\pgfpointxy{3}{11.5}}
	\pgfpathcurveto{\pgfpointxy{6}{11}}{\pgfpointxy{2.5}{7}}{\pgfpointxy{4.5}{5}}
	\pgfpathcurveto{\pgfpointxy{2.5}{7}}{\pgfpointxy{8}{11}}{\pgfpointxy{3}{11.5}}
	\pgfpathcurveto{\pgfpointxy{8}{11}}{\pgfpointxy{2.5}{7}}{\pgfpointxy{4.5}{5}}
	\pgfpathcurveto{\pgfpointxy{2.5}{7}}{\pgfpointxy{2.5}{11}}{\pgfpointxy{3}{11.5}}
	\pgfusepath{fill,stroke}

	% Top
    %     Top-left
	\pgfpathmoveto{\pgfpointxy{-2}{12}}
	\pgfpathcurveto{\pgfpointxy{-2}{12}}{\pgfpointxy{-6}{12}}{\pgfpointxy{-6}{11}}
	\pgfpathcurveto{\pgfpointxy{-5}{9}}{\pgfpointxy{-2}{11}}{\pgfpointxy{-2}{11.85}}
	\pgfpathcurveto{\pgfpointxy{-2}{11.5}}{\pgfpointxy{-4.5}{9.5}}{\pgfpointxy{-6}{11}}
	\pgfpathcurveto{\pgfpointxy{-4.5}{9.5}}{\pgfpointxy{-2}{11.5}}{\pgfpointxy{-2}{11.85}}
	\pgfpathcurveto{\pgfpointxy{-2}{12}}{\pgfpointxy{-3.5}{10.4}}{\pgfpointxy{-6}{11}}
	\pgfpathcurveto{\pgfpointxy{-3.5}{10.4}}{\pgfpointxy{-2}{12}}{\pgfpointxy{-2}{11.85}}

	%    Top-middle
	\pgfpathcurveto{\pgfpointxy{-1}{10.5}}{\pgfpointxy{1}{10.5}}{\pgfpointxy{2}{11.85}}
	\pgfpathcurveto{\pgfpointxy{1}{10.5}}{\pgfpointxy{-1}{10.5}}{\pgfpointxy{-2}{11.85}}	
	\pgfpathcurveto{\pgfpointxy{-1}{11}}{\pgfpointxy{1}{11}}{\pgfpointxy{2}{11.85}}
	\pgfpathcurveto{\pgfpointxy{1}{11}}{\pgfpointxy{-1}{11}}{\pgfpointxy{-2}{11.85}}	
	\pgfpathcurveto{\pgfpointxy{-1}{10}}{\pgfpointxy{1}{10}}{\pgfpointxy{2}{11.85}}
	
	%    Top-right
	\pgfpathcurveto{\pgfpointxy{2}{11.5}}{\pgfpointxy{4.5}{9.5}}{\pgfpointxy{6}{11}}
	\pgfpathcurveto{\pgfpointxy{4.5}{9.5}}{\pgfpointxy{2}{11.5}}{\pgfpointxy{2}{11.85}}
	\pgfpathcurveto{\pgfpointxy{2}{12}}{\pgfpointxy{3.5}{10.4}}{\pgfpointxy{6}{11}}
	\pgfpathcurveto{\pgfpointxy{3.5}{10.4}}{\pgfpointxy{2}{12}}{\pgfpointxy{2}{11.85}}
	\pgfpathcurveto{\pgfpointxy{2}{11}}{\pgfpointxy{5}{9}}{\pgfpointxy{6}{11}}
	\pgfpathcurveto{\pgfpointxy{6}{12}}{\pgfpointxy{2}{12}}{\pgfpointxy{2}{12}}
	\pgfpathclose 
	\pgfusepath{fill,stroke} 

	% Rope
	%     Rope-right
	\pgfsetstrokecolor{black}
	\pgfpathmoveto{\pgfpointxy{-4.5}{5}}
	\pgfpathcurveto{\pgfpointxy{-4.5}{5}}{\pgfpointxy{-6}{5}}{\pgfpointxy{-6}{5.5}}
	\pgfusepath{stroke}	
	%     Rope-left
	\pgfsetstrokecolor{black}
	\pgfpathmoveto{\pgfpointxy{4.5}{5}}
	\pgfpathcurveto{\pgfpointxy{4.5}{5}}{\pgfpointxy{6}{5}}{\pgfpointxy{6}{5.5}}
	\pgfusepath{stroke}
	
	\node[color=black] at (0,0) {{\scalefont{10.0}STAGE}};

	%% Just kinda a pretty path...
	%% \pgfpathmoveto{\pgfpointxy{-2}{1.5}}
	%% \pgfpathcurveto{\pgfpointxy{-2}{1.5}}{\pgfpointxy{-6}{1.5}}{\pgfpointxy{-6}{2.5}}
	%% \pgfpathcurveto{\pgfpointxy{-5}{4.5}}{\pgfpointxy{-2}{2.5}}{\pgfpointxy{-2}{3.35}}
	%% \pgfpathcurveto{\pgfpointxy{-1}{3.5}}{\pgfpointxy{1}{3.5}}{\pgfpointxy{2}{3.35}}
	%% \pgfpathcurveto{\pgfpointxy{2}{2.5}}{\pgfpointxy{5}{4.5}}{\pgfpointxy{6}{2.5}}
	%% \pgfpathcurveto{\pgfpointxy{6}{1.5}}{\pgfpointxy{2}{1.5}}{\pgfpointxy{2}{1.5}}
	%% \pgfpathclose 
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    pdftitle={STAGE Software Requirements Specification v1},
    pdfauthor={Dustin Ingram, Aaron Rosenfeld, Maria Kolakowska, Frank Clark}
}

% So we can number paragraphs too
\setcounter{secnumdepth}{5}

% For headers and footers
\setlength{\headheight}{15pt}
\setlength{\headsep}{25pt}
\pagestyle{fancy}
	
% Page style for the title page
\fancypagestyle{plain}{
    \fancyhf{}
    \renewcommand{\headrulewidth}{0pt}
    \renewcommand{\footrulewidth}{0pt}
}

% Just so we don't have to specify this twice
\newcommand\mytitle{Software Requirements Specification}
\newcommand\mydate{\today}

% Page style for every other page
\fancyhf{} % clear all header and footer fields
\fancyhead[L]{STAGE}
\fancyhead[C]{\mytitle}
\fancyhead[R]{\mydate}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\title{\textbf{\mytitle}}
\author{
	Frank Clark \\\url{francis.j.clark@drexel.edu}
    \and Dustin Ingram \\\url{dustin.s.ingram@drexel.edu}
	\and Maria Kolakowska \\\url{maria.j.kolakowska@drexel.edu}
    \and Aaron Rosenfeld \\\url{aaron.rosenfeld@drexel.edu}
}
\date{\mydate\\Version 1}

\begin{document}
\pagenumbering{roman}

\begin{figure}
    \vspace{-2em}
    \centering
	\begin{tikzpicture}[scale=1]
		\logo
	\end{tikzpicture}
    \vspace{-4em}
\end{figure}

\maketitle

\begin{abstract}
STAGE provides the capability to test the veracity of system-level sensors and component-level algorithms in the laboratory against virtual operations using data from simulated sensors and nodes. These nodes will work with scripted or real time data, depending on the user's need. This network and sensor testbed allows users to independently vary its topology, application suites, and the environment. It also emulates the communication between these components. A visualization tool is provided to the user for demoing and analyzing.
\end{abstract}

\setcounter{tocdepth}{4}
\tableofcontents
\pagebreak
\pagenumbering{arabic}

%\listoftodos

%___________________________________________________________________________

\section{Introduction%
  \label{introduction}%
}

%___________________________________________________________________________

\subsection{Purpose%
  \label{purpose}%
}

This requirements document defines the functional and non-functional requirements for the STAGE project.  These requirements will include, but are not limited to, the performance, interfaces, and hardware goals and limitations.  The information presented here is intended for the development team and the external stakeholders, currently Dr. William Regli, Mr. Joseph B. Kopena, Mr. Joeseph P. Macker, and The U.S. Naval Research Laboratory.

%___________________________________________________________________________

\subsection{Scope%
  \label{scope}%
}

The goal of the STAGE project is to allow for the testing of agents working together on seperate nodes across multiple scenario and topology situations.  STAGE will allow the user to examine how effectively nodes (with agents running on them) interact with one another.  This includes network connections between nodes, the fidelity of these connections, and the proficiency of the agents to process and transmit data.

STAGE consists of six main components: Visualization, Topology, Scenario, Agent Framework, Distribution Framework, and the API.  The Visualization allows the user to see what is happening in the emulation.  For example, network links and their strength, movement of nodes in the virtual world, as well as the movement of non-agent world objects will all have a visual representation over a map of the world.  The Topology will be a scripted language that defines interfaces and network connections on each node.  It will also describe any changes in the network that do not result from mobility.  The Scenario is a scripted language that defines the location and mobility patterns of each node and non-node world object. It will also handle the timing of events. An Agent Framework will indicate the agent(software) running on each node and permit different algorithms to be tested on different nodes.  The Distribution Framework will help distribute the emulation across multiple physical nodes in a cluster.  An API will also be provided to allow the user to interact with the emulation.  For example, it will allow a user to trigger outside events or query information being generated by the emulation. 

Users of STAGE are going to be researchers looking to improve or test their current agent/network interactions across different topology and scenario combinations.  
%___________________________________________________________________________

\subsection{Definitions, Acronyms, and Abbreviations%
  \label{definitions}%
}

\begin{description}
\item[Agent]
	Agents are emulated pieces of software that run on nodes in the network. They will consist of different algorithms that are relevant for the user to test on different scenarios and topolgoies.   

\item[Distribution Framework]
	The distribution framework will facilitate the distribution of the emulation across a multi-platform physical cluster.  This will allow the system to exceed the number of nodes per platform for a single emulation, at the system's discretion.

\item[Node]
	Nodes are virtual or physical machines that consist of agents and network interfaces.  If nodes are virtual, many nodes may run on one physical machine.  

\item[Scenario]
	Scenario will comprise of a scripted language indicating the location and mobility patterns of any emulated nodes within the virtual world. These nodes consist of agents (see definiton of 'Agent') and non-agent world objects such as planes, boats, ground vehicles, etc. 

\item[Topology]
	Topology refers to the network topology between nodes. It will be described with a scripting language.  This language will specify the details of network interfaces on each emulated node, including radio models and throughput characteristics.  It will describe any physical or wireless links that connect these interfaces.  Further, it will indicate changes in linkage over time such as a wireless interface switches wireless LANs or a physical link being created or severed. 

\item[Visualizer]
	The Visualizer will allow the emulations to be superimposed over real-world topography.  This will allow the user to be able to examine the behavior of the agents.  It will also allow for overlays such as link quality, traffic rates, or other metrics deemed important to specific components

\end{description}

%___________________________________________________________________________

% \TODO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Do we have any references? Add them here
\subsection{References%
  \label{references}%
}

These documents explain in-depth about the various technologies involved in this project.
%
\begin{itemize*}
	\item Placeholder Reference: \url{http://www.awesome-reference.com/also/dustin/is/awesome/}
\end{itemize*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\ %

%___________________________________________________________________________

\subsection{Overview%
  \label{overview}%
}

The rest of this document is organized as follows: 
\begin{itemize*}
	\item[-]Section \ref{overall-description} gives a high level overview of the project requirements.  
	\item[-]Section \ref{specific-requirements} gives more detailed project requirements.  
	\item[-]Sections \ref{input-formats} and \ref{output-formats} provides detail in the inputs and outputs of the system, 
	\item[-]Section \ref{functional} specifies what the software will do, 
	\item[-]Section \ref{performance} gives performance requirements for the underlying system.
\end{itemize*}
The rest of Section \ref{specific-requirements} explains other minor requirements.


%___________________________________________________________________________

\section{Overall Description%
  \label{overall-description}%
}

%___________________________________________________________________________

\subsection{Product Perspective%
  \label{product-perspective}%
}

STAGE can be used as a testbed for sensors and respective algorithms in the laboratory against virtual operations using data from simulated sensors and nodes. The ability to independently and quickly vary the network topology, application suites, environment, or any other variable will be essential to collect data which would be cost-prohitive to produce in a real-world scenario. Furthermore, the visualization tool can be used for conceptual demonstrations.

%___________________________________________________________________________

\subsubsection{System Interfaces%
  \label{system-interfaces}%
}

STAGE combines:
\begin{itemize}
    \item Scenario Language - Defining the entire scenario in a very simple language
    \item Agent Framework - Supporting the customization of semi-intelligent agents
    \item Topology Creator - Creating a virtual topology of nodes defined in the Scenario Language
    \item Distribution Framework - Distributing a large-scale emulation across numerous physical machines
    \item Data-Collection API - Collecting all relevant data through a simple API
    \item Visualization Engine - Conceptually visualizing terrain, node movement, link status, etc.
\end{itemize}

%___________________________________________________________________________

\subsubsection{User Interfaces%
  \label{user-interfaces}%
}

STAGE's user interface is two-fold, with each interface for different tasks and uses. The basic interface allows a user to simply and quickly define a scenario with the Scenario Language and begin an experiment, using the API to collect data in a way that is defined by the user. The Visualization Engine allows the user to interpret the experiment visually, without a need for data-collection or the API.

%___________________________________________________________________________

\subsubsection{Hardware Interfaces%
  \label{hardware-interfaces}%
}

STAGE requires that the machine running the system has one to many network interfaces to support distribution.

%___________________________________________________________________________

\subsubsection{Software Interfaces%
  \label{software-interfaces}%
}

STAGE requires the use of Linux Namespaces' kernel virtualization as well as OpenGL in order to use the visualizer.

%___________________________________________________________________________

\subsubsection{Memory Constraints%
  \label{memory-constraints}%
}

STAGE requires a machine with at least 4GB of RAM.

%___________________________________________________________________________

\subsubsection{Site Adaptation Requirements%
  \label{site-adaptation-requirements}%
}

STAGE requires that the system is configured per-site to create a distributed emulation, or to interact on-the-fly.

%___________________________________________________________________________

\subsection{Product Functions%
  \label{product-functions}%
}

This software is a testbed, where the user specifies an environment, network configuration, and applications to run in the scenario. Each of these items may be varied independently.

The general function of this software is to run a simulation.  The software collects data as it runs, which can then be used to evaluate the combination of items previously mentioned.  This is essential to research, as having this data helps to analyze the behavior of the applications that are running within the scenario.

There also exists a visualization component of the software. The simulation can run without it, however, it is a useful tool when trying to quickly summarize the current simulation state.  The visualization uses data from the environment configuration to display various types of terrain.

The simulation runs in real time.  This allows for realistic simulations, where humans may interfere with self-directing agents in the application. There exists other simulation software which can display a scripted demo, however, this does not allow for realistic human intervention.  Real-time simulations are necessary for training simulations.

The environment that is specified will contain terrain data and static world objects, so that it may mirror existing real-world locations.  This is useful for testing the  effectiveness of agent behavior in real-world situations, such as trying to get rovers to secure a given range of city blocks in Philadelphia. Though it may be of some benefit to test this with random mazes, it is more useful to test in an environment that models the real world.

The user specifies the initial network configuration, i.e. the types of connections and which agents are connected in the simulation.  This network is simulated, and its configuration may change over time. For example, if two agents that have a Wi-Fi connection move too far away from each other, their connection ceases to exist. 

%___________________________________________________________________________


\subsection{User Characteristics%
  \label{user-characteristics}%
}

The system has four different types of users.  Each type of user has different goals and needs to use different parts of the system.  These user roles, while they may be performed by the same user, are here split into the four distinct roles for clairty:

%___________________________________________________________________________

\subsubsection{User: Alice, Project Manager%
  \label{alice}%
}

Alice uses STAGE for demonstrations and to acquire funding for research.  Alice wants to complete the tasks below with
the visualization:

\begin{itemize*}
    \item Start a simulation
    \item View the simulation in real or simulated time
    \item Move the viewpoint
    \item Visualize simulation events including link changes and entity movements
    \item View output from agents if implemented
\end{itemize*}

\subsubsection{User: Bob, Agent Algorithm Researcher%
  \label{bob}%
}

Bob researches agent algorithms and uses STAGE to compare their effectiveness.  Bob wants to complete the tasks below:

\begin{itemize*}
    \item Use the API to implement agents which run on network nodes
    \item Use the visualizer to assure scenarios are properly setup
    \item Disable the visualizer and run scenarios many times
    \item Collect aggregate data from scenario trials
\end{itemize*}

\subsubsection{User: Carol, Network Protocol Developer%
  \label{bob}%
}

Carol uses STAGE to test networking protocols.  Specifically, she tries different network protocols with a single agent
setup to find the best combination.  Carol wants to complete the tasks below:

\begin{itemize*}
    \item Use the networking component to implement networking protocols
    \item Disable the visualizer and run scenarios many times
    \item Collect aggregate data from scenario trials
\end{itemize*}

\subsubsection{User: Dave, Large Scale Simulator%
  \label{bob}%
}

Dave uses STAGE to run large scale simulations which run slower than real-time on his personal computer.  Dave wants to
complete the tasks below:

\begin{itemize*}
    \item Distribute agent instances to multiple physical machines
    \item Abstract the physical links from the simulation
    \item Coordinate data collection after simulations
\end{itemize*}
%___________________________________________________________________________

\subsection{Constraints%
  \label{constraints}%
}

The system must be able to interpret and/or process any agent or topology it is given.  If this isn't possible for any reason, the system should inform the user of this. No piece of this system requires elevated privileges.

%___________________________________________________________________________

\subsection{Assumptions and Dependencies%
  \label{assumptions-and-dependencies}%
}

It is assumed that a user, administrator, or developer has the ability to install required libraries which will named in the future as a result of the development process.

%___________________________________________________________________________

\section{Specific Requirements%
  \label{specific-requirements}%
}

\subsection{Functional Requirements%
    \label{functional}%
}

\subsubsection{Visualization}
\paragraph{Node Position} The visualization shall display the physical location of network nodes.
\paragraph{Entity Position} The visualization shall display the physical location of entities other than network nodes.

\subsubsection{Topology Definition}
\paragraph{Interfaces} The network definition language shall specify interfaces on each virtual node.  Specifically,
each interface shall be described with a physical model (radio, wired, etc.) and an appropriate link-layer protocol.

\paragraph{Networks} The network definition language shall specify networks to which interfaces may interact.  Networks
are described with a unique identifier and physical layer model (e.g. radio propagation model).

\paragraph{Links} The network definition language shall specify one-to-one links between interfaces.  A link is
described by a physical layer model.

\subsubsection{Scenario Definition}
\paragraph{Location} The scenario definition language shall define the location of agent and non-agent world objects
\paragraph{Mobility} The scenario definition language shall describe the mobility or each virtual node as a function of
time.
\paragraph{Events} Mobility shall be alterable as a result of events, specified in the scenario definition.
\paragraph{Non-node Behavior} The scenario definition language shall describe the movement of and events triggered by
entities other than virtual nodes.

\subsubsection{Agent Framework}
\paragraph{Agent Location} The agent framework shall specify on which virtual node(s) a given agent should operate.
\paragraph{Startup} The agent framework shall specify the startup parameters of each agent.
\paragraph{Collection} The agent framework shall specify the output parameters of each agent instance.

\subsubsection{Distribution Framework}
\paragraph{Physical Distribution} The distribution framework shall distribute virtual nodes evenly across physical
nodes.  Further, it shall handle the establishment of agents on the proper physical node.

\paragraph{Data Collection} The distribution framework shall aggregate simulation data at the end of a trial.

\paragraph{Simulation Server} The distribution framework all organize physical nodes to interact with the simulation
server.

%___________________________________________________________________________

\subsubsection{Data Storage%
  \label{data-storage}%
}
    \paragraph{Outside Databases} No outside database system will be used for data storage, unless it is introduced by the user via the API
    \paragraph{Scenario Definitions} Scenario definitions, including the topology and agents, will be stored and parsed by the system

%___________________________________________________________________________

\subsection{Runtime Environment} 
\begin{itemize*}
    \item Operating Systems:  Unix / Linux / Mac
    \item Processor:  A 32- or 64-bit x86 3.0GHz processor
    \item Memory:  4GB RAM minimum
    \item Network connection:  Any recent network card which is currently connected to the emulation network (if the emulation is distributed)
    \item Visualizer:  A graphics card which will support OpenGL or an equivalent
\end{itemize*}

%___________________________________________________________________________

\subsection{Input Formats%
  \label{input-formats}%
}

\subsubsection{Scenario}
    \paragraph{Location Data} The simulation shall be able to read location data for nodes.
	\paragraph{Mobility Data} The simulation shall be able to read mobility data for nodes.
	\paragraph{Scenario Input} The simulation shall be able to respond to event input from scenario input files

\subsubsection{Topology}
    \paragraph{Network Interfaces} The simulation shall be able to read network interfaces for nodes
    \paragraph{Network Links} The simulation shall be able to read links in the network between interfaces
    \paragraph{Network Topology} The simulation shall be able to read changes to the network topology

% NOTE: Believe we settled on no Network input.
%\subsubsection{Network}
%\begin{enumerate}
%		\item Nodes designated by the Topology shall be able to read in 802.11 (Wireless) traffic
%		\item Nodes designated by the Topology shall be able to read in TCP traffic
%		\item Nodes designated by the Topology shall be able to read in UDP traffic
%\end{enumerate}

%___________________________________________________________________________

\subsection{Output Formats%
  \label{output-formats}%
}

    \paragraph{Network Changes} The system shall support outputting network data changes over time post-simulation
    \paragraph{Network Fidelity} The system shall support outputting network fidelity over time post-simulation
	\paragraph{Topology Changes} The system shall support outputting topology changes over time post-simulation
	\paragraph{Mobility Patterns} The system shall support outputting agent and non-agent mobility patterns post simulation

%___________________________________________________________________________

\subsection{User Interface%
  \label{user-interface}%
}

The following applies to STAGE's basic interface:
    \paragraph{Scenario} The interface allows a user to define a scenario.
    \paragraph{Scenario Language} The scenario that will be defined by the interface will be written in the Scenario Language.
    \paragraph{Beginning Experiment} The interface allows a user to begin an experiment.
    \paragraph{Ending Experiment} The interface allows a user to end an experiment.

The following applies to STAGE's Visualization Engine (VE):
    \paragraph{Terrain} The VE will display varying types of terrain, as defined by the environment.
    \paragraph{World Objects} The VE will display mobile and static world objects, as defined by the scenario.
    \paragraph{Mobile Agents} The VE will display mobile agents.
    \paragraph{Pathfinding} The VE will find the path for an object to move to a given coordinate, if there are no objects between it and the destination.
    \paragraph{Maximum Models} The VE is able to display 300 models in a given scenario.
    \paragraph{Limitations of Movement} The VE limits the movement of models to specific areas or types of terrain (e.g. boats may only move on river).
    \paragraph{Modularity} The VE component is modular, i.e. it can be removed from the framework without affecting functionality (with the exception of the visuals).
    \paragraph{Timing} The VE runs in real-time.
    \paragraph{Viewpoints} The VE is able to display the world from more than one point of view.
    \paragraph{Viewpoints} The VE is able to display the world from any given point of view.

%___________________________________________________________________________

\subsection{Extensibility%
  \label{extensibility}%
}
    \paragraph{Custom Topologies} The system shall provide a means for users to create custom topologies.
    \paragraph{Custom Agents} The system shall provide a means for users to create custom agents.

\subsection{Testing%
    \label{testing}%
}
All code with in the system must be tested. Core functionality of the software will have 100\% code coverage with automated unit and integration tests.  The visualizer testing will be done manually as it is a smaller component and would otherwise require a disproportionately large investment in initial setup.  Unit tests will cover the algorithms used in our system while integration tests will be used to test our data-flow.  

\section{System Evolution}

With more time, the STAGE team could create additional tools to aid in the the development of more complex agents or topologies, so that user customization does not become too granular.  Furthermore, tools which can automate or assist in data collection and parsing could be implements.  Even further development could lead to a platform that included Windows or other operating systems.

%___________________________________________________________________________

% \TODO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is particularly relevant! Real (emulated) time vs. simulated time!
\subsection{Performance%
    \label{performance}%
}

%___________________________________________________________________________

\subsubsection{Real Time}\label{realtime} 
% \TODO
TODO

%___________________________________________________________________________

\subsubsection{Non-Real Time}\label{nonrealtime}
% \TODO
TODO
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\ %

%___________________________________________________________________________

\subsection{Documentation%
  \label{documentation}%
}
\begin{enumerate}
    \item The software shall provide a User Manual containing step-by-step instructions for user perspective in Section~\ref{user-characteristics}.
    \item The software shall provide Developer Documentation containing:
    \begin{enumerate}
        \item Agent Framework definitions and example agents
        \item Scenario Language syntax and usage
    \end{enumerate}
\end{enumerate}

%___________________________________________________________________________

\appendix
\pagebreak

\end{document}
